\large{\bf Large effects and the infinitesimal model }

### 2023-11-27 writeup.tex
notes from meeting

>>>>

\comment{Make the point that another way to think about distibutions with non-finite variance
    is that there's only a finite number of alleles above any fixed value;
    and also the variance in any finite population will be finite.
    (see reviewer comment, ``all the empirical trait distributions they find have mean and variance'')
    Also discuss comparison to fat-tailed dispersal:
    the question is, what distribution gives us a better model?
    For dispersal, a fat-tailed distribution has in practice finite variance
    but is a better model in that it describes noisiness better;
    here, the analogy is something about polygenicity and noisiness of the process of adaptation.
    If we're modeling non-polygenic (oligogenic) traits then
    why stable as opposed to some other arbitrary distribution?
    Well, the distribution of per-allele effect sizes might not be stable, but CLT tells us that maybe
    stable gives a good approx to the process (as in Gaussian case).
}
